---
title: "rvalidate"
date: "`r Sys.Date()`"
output:
  html_document:
    keep_md: TRUE

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
devtools::load_all()
# options(kableExtra.table.format = "html")
```


## Table of Contents
1. [Introduction](#intro)
2. [Residual tables](#2)
3. [Residual plots](#3)
4. [Coverage tables](#4)
5. [Statistics for multiple observations per group](#5)

## <a name="intro"></a>
## Introduction
rvalidate computes and presents validation statistics based on model results. All you need to do is set up a tibble composed of model results and observed data. This step is exemplified below. The package does the rest of the work. Validation statistics include residuals `rvalidate::residuals`, coverage `rvalidate::coverage`, and Probability integral transforms `rvalidate::pit`. We do not stylize the output of our functions. This can be customized based on user prefference with a package such as `kableExtra`

User input data should be formated as our simulated data `rvalidate::data`.
```{r}
library(rvalidate)
rv_data %>% head() %>% kableExtra::kable()
```



## <a name="2"></a>
## residual tables
This function supports reporting of residual for subsets within the data. Subset arguement is NULL by default and will not report for subsets when unspecified.
```{r, warning = FALSE}
library(rvalidate)
residuals(data = rv_data,
           y = "y",
           yhat = "50%",
           total_standard_error = "total_sd") %>%
  kableExtra::kable() %>%
  kableExtra::column_spec(1, bold = T) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top")
```

```{r, warning = FALSE}
residuals(data = rv_data,
           y = "y",
           yhat = "50%",
           total_standard_error = "total_sd",
           subset = "source")  %>%
  kableExtra::kable() %>%
  kableExtra::column_spec(1:2, bold = T) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top")
```

```{r, warning = FALSE}
residuals(data = rv_data,
           y = "y",
           yhat = "50%",
           total_standard_error = "total_sd",
           subset = c("source", "region_code")) %>%
  kableExtra::kable() %>%
  kableExtra::column_spec(1:3, bold = T) %>%
  kableExtra::collapse_rows(columns = 1:2, valign = "top")
```


## <a name="3"></a>
## Residual plots
```{r}
residuals_autoplot(
  data = rv_data,
  y = "y",
  yhat = "50%"
)
```


## <a name="4"></a>
## Coverage tables
If provided a subset column name, coverage will be calculate for each subset.
```{r}
coverage(data = rv_data,
         y = "y",
         lower = "2.5%",
         upper = "97.5%",
         subset = "source")  %>%
  kableExtra::kable() %>%
  kableExtra::column_spec(1, bold = T)
```

## <a name="5"></a>
## Statistics for data with multiple observations within a grouping
For data containing multiple observations per group (e.g. country-year you) we compute statistics for all unique permutations of the data where there is only one observation from each group in each permutation. Note the run time will increase substantially as the number of multiple observations increase.

### residual
```{r}
devtools::load_all()
residuals_multiple(data = rv_data,
           y = "y",
           yhat = "50%",
           total_standard_error = "total_sd",
           subset = "source",
           group_to_check = c("country_code", "year"))  %>%
  kableExtra::kable() %>%
  kableExtra::column_spec(1:2, bold = T) %>%
  kableExtra::collapse_rows(columns = 1:2, valign = "top")
```

### Coverage
```{r}
coverage_multiple(data = rv_data,
         y = "y",
         lower = "2.5%",
         upper = "97.5%",
         subset = "source",
         group_to_check = c("country_code", "year"))  %>%
  kableExtra::kable() %>%
  kableExtra::column_spec(1, bold = T)

```
