---
title: "rvalidate"
output:
   html_document:
      self_contained: false
      keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# library(cetable)
devtools::load_all()
```


## Table of Contents
1. [Introduction](#intro)
2. [Error tables](#2)
3. [Coverage tables](#3)
  
## <a name="intro"></a>
## Introduction
rvalidate computes validation statistics for models and draw up aesthetic tables and plots. Supports error, coverage, and Probability integral transforms. Input data should be formated as our simulated data. See `rvalidate::rv_data`
```{r}
rv_data %>% head()
```


## <a name="2"></a>
## Error tables
```{r}
rv_error(data = simdata, 
           parameter = "observed_value", 
           estimate = "50%", 
           total_standard_error = "totalerror_sd",
           subset = "source")  %>%
  kableExtra::kable() %>%
  kableExtra::column_spec(1:2, bold = T) %>%
  kableExtra::collapse_rows(columns = 1:2, valign = "top")
```

## <a name="3"></a>
## Coverage tables
If provided a subset column name, coverage will be calculate for each subset.
```{r}
rv_coverage(data = simdata, 
         parameter = "observed_value", 
         lower = "2.5%", 
         upper = "97.5%", 
         subset = "source")  %>%
  kableExtra::kable() %>%
  kableExtra::column_spec(1, bold = T)
```



## <a name="3"></a>
## Coverage tables for data with multiple observations within a grouping
```{r}
rv_coverage_multiple(data = simdata, 
         parameter = "observed_value", 
         lower = "2.5%", 
         upper = "97.5%", 
         subset = "source",
         group_to_check = c("country_code", "year"))  %>%
  kableExtra::kable() %>%
  kableExtra::column_spec(1:2, bold = T) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top")

```

